---
title: "Untitled"
author: "Narjes Mathlouthi"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv(here("data","slo_homes.csv"))
#think about the relationships you expect to exist
# home price sign 
#unique(homes$City)
```

### Create a subset with 4 cities

Task: create a subset (called homes_subset) that only contains observations where the city is:

- "San luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo","Atascadero","Arroyo Grande", "Santa Maria-Orcutt"))

# if you use == it will look at elements (observations)in a column one by one in the order listed in the vector 
#check what the code is doing or your results

#unique(homes_subset$City)
```


###

```{r, include = FALSE, eval=FALSE}

homes_table <- homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(
    mean_price = mean(Price),
    sd_price = sd(Price),
    mean_sqft = mean(PricePerSqFt),
    sample_size = n()
    )
homes_table

# eval=FALSE complete doesn't run the code at all/ include = FALSE is still running the code

```

Task: explore the relationship between square footage and home price(from homes_subset) in a scatterplot

```{r}
ggplot(data = homes_subset, aes(x = SqFt , y = Price)) +
  geom_point() +
  #to add abline to see
  geom_smooth(method ="lm")
         
#initial takeaway : linear relationship with positive correlation
#The outlier of 5M missing vars such as how big is the land or other #characteristics that could explain the outlier 
#Think about what might explain the outlier (data point) & dont get rid of it.
#Pretty large sample that's dominating (n =400) compare to 1 outlier 
# We expect larger houses to have higher sales 
# We can get a better sense of how the vars that we do have do relate even though we re missing important vars suchas property size and home age
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictator vars and home Price, using home_subset

Create 2 different permutations of this model:
(1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price ~ City, SqFt, Status (lm2)
(3) Try another one (lm3)

For Santa Maria Orcutt: 
If the homes are otherwise similar, I would expect that homes in Santa Maria Orcutt would be on average 260860.77 

```{r}
#Bedrooms is a continous var. In model 1,  as bathrooms # increases price decreases
#A*****djusted R-squared meaning =>  53% (how much of the variance in the dependent variable) of home price is explained by the vars in the model. 

# TESTING THE NULL hypothesis of testing 


model1 <- lm(Price ~ City + Bedrooms + Bathrooms +SqFt + Status, data = homes_subset)
model2 <- lm(Price ~ City + SqFt + Status, data = homes_subset )
model3 <- lm(Price ~ City + SqFt + Status + Bathrooms, data = homes_subset)

#If I wanted San Luis Obispo to be the reference level:
#Use fct_relevel to specify a new reference level

new_homes_subset <- homes_subset %>% 
  mutate(City =fct_relevel(City, "San Luis Obispo"))
# this will make slo teh reference level
lm_slo <- lm(Price ~ SqFt + City, data = homes_subset)

summary(model1)



```


### Explore correlations between quantitative variables 

Task : make a subset called homes_quant(starting from homes_subset) that only contains vars from Price through SqFT

```{r}
homes_quant <-  homes_subset %>% 
  select(Price:SqFt)

#Check the colinearity of the vars
# SQqFT has the highest correlation
homes_cor <- cor(homes_quant)

corrplot(homes_cor, method="ellipse")

summary(model2)

```
### Compare AIC values




```{r}
AIC(model1)
AIC(model2)
AIC(model3)

#lower AIC is better
```


### Use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(model1,model2,model3))

#SqFT stays pretty close 
```

### Check out diagnostic plots

```{r}

plot(model1)

#3rd plot is position in teh data frame
#cook's distance plot 
```



### Use broom::augment() to return the predictions for existing observations

```{r}
home_predictions <- augment(model1)
# Make a histogram of the residuals from thsi model
ggplot(data = home_predictions, aes(x= .resid)) +
  geom_histogram()
# follows a normal distributions
```

# Branches are awesome



